\texorpdfstring{\ZpL}{ZpL}: a p-adic precision package

### 2018-05-08 ZpL/ZpL.tex
8 pages

The article is structured as follows. In \S \ref{sec:demo} we provide a demonstration
of the package, showing how it can provide more precise answers than the
traditional methods for tracking $p$-adic precision.  In particular, \S \ref{ssec:elem}
describes elementary arithmetic and the SOMOS-4 sequence, \S \ref{ssec:linalg}
gives examples from linear algebra, \S \ref{ssec:comalg} examples using polynomials,
and \S \ref{ssec:diffeq} examples of differential equations.

In \S \ref{sec:implementation} we give more details on the implementation.
\S \ref{ssec:preclemma} contains a brief overview on the theory of
$p$-adic precision of \cite{caruso-roe-vaccon:14a}. 
In the next two subsections, we explain in more details how our package
works. \S \ref{ssec:trackprec} is devoted to the implementation of 
automatic differentiation leading to the actual computation of the
module that models the precision.
In \S \ref{ssec:viewprec}, we explain how precision on any individual number
can be recovered and discuss the validity
of our results.
The complexity overhead induced by our package is analyzed in
\S \ref{ssec:complexity}.
Finally, \S \ref{sec:conclusion} contains a discussion of how we see this
package fitting into the existing $p$-adic implementations.  While these
methods do introduce overhead, they are well suited to exploring
precision behavior when designing algorithms, and can provide
hints as to when further precision analysis would be useful.

@@

\noindent
\ZpXX is a generic notation for \ZpCR, \ZpLC and \ZpLF.
The first, \ZpCR, is the usual constructor for $p$-adic parents in 
\sage. It tracks 
precision using interval arithmetic. The parents 
\ZpLC and \ZpLF provided by our package\footnote{\text{\color{output} \rm \tt CR} stands for \textit{capped relative},
\text{\color{output} \rm \tt LC} for \textit{lattice-cap}, and \text{\color{output} \rm \tt LF} for \textit{lattice-float}.}
track precision differently; more details will be provided in Section \ref{sec:implementation}.
In the sequel, we will compare the outputs provided by each parent.
As the results for \ZpLF and \ZpLC agree on all examples in this section, 
we will only give those for \ZpLC.

>>>>

The article is structured as follows. In \S \ref{sec:demo} we provide a demonstration
of the package, showing how it can provide more precise answers than the
traditional methods for tracking $p$-adic precision.  In particular, \S \ref{ssec:elem}
describes elementary arithmetic and the SOMOS-4 sequence, \S \ref{ssec:linalg}
gives examples from linear algebra, \S \ref{ssec:comalg} examples using polynomials,
and \S \ref{ssec:diffeq} examples of differential equations.
In \S \ref{sec:implementation} we give more details on the implementation.
\S \ref{ssec:preclemma} contains a brief overview on the theory of
$p$-adic precision of \cite{caruso-roe-vaccon:14a}. 
%In the next two subsections, we explain in more details how our package
%works.
\S \ref{ssec:trackprec} is devoted to the implementation of 
automatic differentiation leading to the actual computation of the
module that models the precision.
In \S \ref{ssec:viewprec}, we explain how precision on any individual number
can be recovered and discuss the validity
of our results.
The complexity overhead induced by our package is analyzed in
\S \ref{ssec:complexity}.
Finally, \S \ref{sec:conclusion} contains a discussion of how we see this
package fitting into the existing $p$-adic implementations.  While these
methods do introduce overhead, they are well suited to exploring
precision behavior when designing algorithms, and can provide
hints as to when further precision analysis would be useful.

@@

\noindent
\ZpXX is a generic notation for \ZpCR, \ZpLC and \ZpLF.
The first, \ZpCR, is the usual constructor for $p$-adic parents in 
\sage. It tracks 
precision using interval arithmetic. The parents 
\ZpLC and \ZpLF provided by our package
%\footnote{\text{\color{output} \rm \tt CR} stands for \textit{capped relative},
%\text{\color{output} \rm \tt LC} for \textit{lattice-cap}, and \text{\color{output} \rm \tt LF} for \textit{lattice-float}.}
track precision differently; more details will be provided in Section \ref{sec:implementation}.
In the sequel, we will compare the outputs provided by each parent.
As the results for \ZpLF and \ZpLC agree on all examples in this section, 
we will only give those for \ZpLC.
